---
title: "2024_ple.27.7fg_assessment"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plaice (*Pleuronectes platessa*) in divisions 7.fg (Bristol Channel, Celtic Sea) - WGCSE 2024

This repository recreates the stock assessment for plaice (*Pleuronectes platessa*) in divisions 7.e (Bristol Channel, Celtic Sea) in `R` from WGCSE 2024.

The advice for this plaice stock is biennial and was last given one year ago at WGCSE 2022. This repository (2024) is a new assessment.

## R packages

The following R packages from CRAN are required to run the assessment:

```{r, eval = FALSE}
icesTAF
icesAdvice
dplyr
tidyr
ggplot2
cat3advice
```

They can be installed with:

```{r, eval = FALSE}
### install/update packages
install.packages(c("icesTAF", "icesAdvice", "dplyr", "tidyr", "ggplot2"))
### install cat3advice from ICES r-universe
install.packages("cat3advice", repos = c("https://ices-tools-prod.r-universe.dev", "https://cloud.r-project.org"))
```

## Running the assessment

The easiest way to run the assessment is to clone or download this repository, navigate into the repository with R and run:

```{r, eval = FALSE}
### load the icesTAF package
library(icesTAF)
### load data
taf.boot()
### run all scripts
source.all()
```

This code snippet runs the data compilation and assessment and creates the tables and figures presented in the WG report.
